A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-19 paper.tex
(0,2) done

\begin{prop}
The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the fields of 8d $\cN=1$ super Yang--Mills are
\begin{align*}
S^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) + t\Omega^{-1} F_{2, 0}\wedge B^* \\
S^{(2)}(Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + tac^*\right) + \frac{t}{2}\Omega^{-1}B^*\wedge B^* .
\end{align*}
\end{prop}

@@

\begin{theorem}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$representation-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$. Moreover, the equivalence is $\U(2)$-equivariant.
\end{theorem}

@@

\begin{theorem}
Fix the twisting datum $\alpha = \alpha_n$. The holomorphic twist of 4d $\cN=2$ super Yang--Mills is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1] \Sect(M, (U\otimes K_M^{1/2}[2n])\ham \fg)$. Moreover, the equivalence is $\MU(2)$-equivariant.
\label{thm:4dholomorphictwist}
\end{theorem}
\begin{proof}
4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory. Under dimensional reduction the 6d fields from Section \ref{sect:6dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \Tilde{a} \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
B&\rightsquigarrow B, b \\
\rho&\rightsquigarrow \rho, \Tilde{\chi} \\
\psi & \rightsquigarrow \psi, \varsigma . \\
\end{align*}

@@

\vspace{-10pt}
\paragraph{Fields:} In the notation of Section \ref{sect:4d_2_holomorphictwist}, the BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
\item Scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)[-2]$ and $a \in\Omega^{0}(M; \gg)[2]$;
\item Gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[-1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[-1]$.
\item Matter bosons $\nu\in\Omega^{0, 1}(M; \fg)$, $\phi\in\Omega^{1,0}(M; \fg)$.
\item Matter fermions $\psi \in \Omega^{1,1} (M;  \fg)[-1]$, $\varsigma \in \Omega^{1,0} (M ; \fg)[1]$, $\Tilde{\nu} \in \Omega^{0,1}(M; \fg)[1]$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(3;\CC)$.  The fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
 \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
 \item $\gg$-valued fermions: $\lambda \otimes u \in \Omega^0(\RR^3 ;  S \otimes W \otimes \fg)$.
 \item $R$-valued fermions: $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus S \otimes R^*)$.
 \item Ghost: $c \in \Omega^0(\RR^3; \gg)[1]$.
\end{itemize}

@@

\vspace{-10pt}
\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\spin(3;\CC)$.  The fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
 \item $U$-valued bosons: a $W$-valued scalar field $(\phi \otimes v) \in \Omega^0(\RR^3; W \otimes U)$.
 \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes (W \oplus W) \otimes \gg)$.
 \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
 \item Ghost field: $c \in \Omega^0(\RR^3; \gg)[1]$.
\end{itemize}

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=8$ supersymmetric Yang--Mills theory by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\spin(3;\CC)$.  
The fields are:
\begin{itemize}
 \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and scalar fields $\phi_j \in \Omega^0(\RR^3; \gg)$, $j=1,\ldots, 7$.
 \item Fermions: spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$, $i=1,\ldots, 8$.
 \item Ghost Field: $c \in \Omega^0(\RR^3;\gg)[1]$.
\end{itemize}

@@

\section{Dimension 2}
The odd part of the $2$-dimensional supersymmetry algebra is $\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_-$.
The comlpex semispin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality.

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(2;\CC)$.  
In any case, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(a, \Bar{a}) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
 \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
 \item $\gg$-valued fermions: $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; (S_+ \otimes W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
 \item $R$-valued fermions: $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus (S_+ \oplus S_-) \otimes R^*)$.
 \item Ghost field: $c \in \Omega^0(\RR^2; \gg)[1]$.
\end{itemize}

@@

\begin{theorem} \label{2d_minimal_twist_thm}
The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.  Moreover, this equivalence is $\mr U(1)$-equivariant.
\end{theorem}

@@

\begin{itemize}
\item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $a \in \Omega^0(\CC ; \fg)[2]$, $\Tilde{a} \in \Omega^0(\CC ; \fg)[2]$. 
\item $\gg$-valued fermions: $\lambda_0 \in \Omega^{0}(\CC ; \fg)[-1]$, $\chi_{0,1} \in \Omega^{0,1}(\CC ; \fg) [1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg)[1]$, $\Tilde{\lambda}_0 \in \Omega^0(\CC ; \fg) [3]$.
 %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
 \item  $R$-valued bosons: $\gamma_0 \in \Omega^0(\CC ; R)$, $\phi \in \Omega^0(\CC ; R^*)$;
 %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
 \item $R$-valued fermions: $\gamma_{0,1} \in \Omega^{0,1}(\CC ; R)[-1]$, $\Tilde{\psi}_0 \in \Omega^0(\CC ; R)[1]$, $\beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)[-1]$, $\psi \in \Omega^0(\CC ; R^*)[1]$; 
 \item Ghost field: $c \in \Omega^0(\RR^2; \fg)[1]$.
\end{itemize}
%We write the antifields similarly: the antifield of a field $x_n$ is written $x^*_{-n}$, with opposite $\mr U(1)$-weight.

@@

\begin{theorem} \label{2d_2_A_twist_thm}
The topological 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory with respect to the family of square-zero supercharges $Q_t$ is perturbatively equivalent to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.  
This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\begin{theorem} \label{2d_2_B_twist_thm}
The topological B-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$.  This equivalence is $\mr U(1)$-invariant.
\end{theorem}

\begin{proof}
We dimensionally reduce the holomorphic twist of 3d $\mc N=2$ super Yang-Mills in a non-invariant direction.  
Combining Theorem \ref{3d_minimal_twist_thm} and Proposition \ref{CS_diml_red_prop} to turn the we obtain the desired result.
\end{proof}

@@

The R-symmetry group is $G_R = \SU(2) \times \spin(4;\CC)$ whose action on $\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_-$ can be described as follows.
First, $\spin(4;\CC)$ acts on $W_+$ and $W_-$ by the fundamental and anti-fundamental representations, respectively.
The group $\SU(2)$ acts by permuting the two factors.

@@

\begin{theorem}
The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$. This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\begin{theorem}
The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ admits a one-parameter deformation to the A-twist.  This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.   This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\begin{theorem}
The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.  This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\begin{prop}
There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra, which we will refer to as the A- and B-supercharges.  The B-supercharge occurs as a degeneration of A-type supercharges.
\end{prop}

\begin{proof}
Our aim is to understand the classification of $\spin(8;\CC)$-orbits in the space of pairs of non-zero null-vectors $w_+ \in W_+$ and $w_- \in W_-$.  Since $\spin(8;\CC)$ acts transitively on the possible choices of $w_+$, it remains for us to understand the action of the stabilizer $\stab(w_+) \sub \spin(8;\CC)$ on the space of null vectors $w_-$.  The element $w_+$ is equivalent to the data of a Lagrangian subspace $L \sub V_8$, along with a half-density.  As a representation of the subgroup $\mr{ML}(L)$ of $\stab(w_+)$, the two semispin representations decompose as
\begin{align*}
 W_+ &\iso (\CC \oplus \wedge^2 L \oplus \wedge^4 L) \otimes \det(L)^{-1/2} \\
 W_- &\iso (L \oplus \wedge^3 L) \otimes \det(L)^{-1/2},
\end{align*}
with $w_+ \in \wedge^4 L$.  With respect to this decomposition, say $w_- = (v_1,v_3)$.  If $v_1 \ne 0$, then we can act by $\wedge^2 L \sub \stab(w_+)$ to make $v_3 = 0$.  Under the action of $\SL(L)$ all such non-zero $v_1$ are in the same orbit.  Likewise if $v_1 = 0$ then $v_3 \ne 0$ and we can act by $\SL(L)$ to see that all such non-zero $v_3$ are in the same orbit.  There are, therefore, two orbits once again, with one degenerating to the other.
\end{proof}

Upon dimensional reduction from 3d $\mc N=8$, the B-supercharge reduces to the 2d $\mc N=(8,8)$ B-supercharge.  Indeed, if we forget down to $\mc N=4$ supersymmetry, then the B-twist should correspond to the B-twist.  In both $\mc N=(4,4)$ and $\mc N=(8,8)$ the two orbits are distinguished, in that the orbit of B-twists lies in the closure of the orbit of A-twists.

@@

\begin{theorem}
The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills admits a one-parameter deformation to the A-twist.  This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.   This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

We consider $\cN=(0,2)$ super Yang-Mills for a Lie algebra $\fg$ coupled to $\cN=(0,2)$ supersymmetric matter. 
The supersymmetric matter consists of the $\cN = (0,2)$ chiral multiplet with values in a representation $R$.

The untwisted fields are given by:
\begin{itemize}
\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
\item $R \oplus R^*$-valued scalars: $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
\item a pair of $R \oplus R^*$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R)$.
\end{itemize}
Here, $W$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
Choose the basis $\{u,v\}$ for $W_-$ with pairing given by $\<u, v\> = 1$.

We will twist by an element $Q = q \otimes u \in S_- \otimes W_-$.

>>>>

\begin{prop}
The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the fields of 8d $\cN=1$ super Yang--Mills are
\begin{align*}
S^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} \Tilde{a}, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) + t\Omega^{-1} F_{2, 0}\wedge B^* \\
S^{(2)}(Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + tac^*\right) + \frac{t}{2}\Omega^{-1}B^*\wedge B^* .
\end{align*}
\end{prop}

@@

\begin{theorem}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$-representation-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$. 
Moreover, the equivalence is $\U(2)$-equivariant.
\end{theorem}

@@

\begin{theorem}
Fix the twisting datum $\alpha = \alpha_n$. The holomorphic twist of 4d $\cN=2$ super Yang--Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1] \Sect(M, (U\otimes K_M^{1/2}[2n])\ham \fg)$. Moreover, the equivalence is $\MU(2)$-equivariant.
\label{thm:4dholomorphictwist}
\end{theorem}
\begin{proof}
4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory. Under dimensional reduction the 6d fields from Section \ref{sect:6dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \Tilde{a} \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
B&\rightsquigarrow B, b \\
\rho&\rightsquigarrow \rho, \Tilde{\chi} \\
\psi & \rightsquigarrow \psi, \varsigma . \\
\end{align*}

@@

\vspace{-10pt}
\paragraph{Fields:} In the notation of Section \ref{sect:4d_2_holomorphictwist}, the BRST fields are given by:
\begin{itemize}
\item gauge bosons $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$, $\Tilde{a} \in \Omega^{0}(M; \gg)[-2]$ and $a \in\Omega^{0}(M; \gg)[2]$;
\item gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[-1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[-1]$.
\item matter bosons $\nu\in\Omega^{0, 1}(M; \fg)$, $\phi\in\Omega^{1,0}(M; \fg)$.
\item matter fermions $\psi \in \Omega^{1,1} (M;  \fg)[-1]$, $\varsigma \in \Omega^{1,0} (M ; \fg)[1]$, $\Tilde{\nu} \in \Omega^{0,1}(M; \fg)[1]$.
\item a ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(3;\CC)$.  The fields we obtain are
\begin{itemize}
 \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
 \item matter bosons $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
 \item gauge fermions $\lambda \otimes u \in \Omega^0(\RR^3 ;  S \otimes W \otimes \fg)$.
 \item matter fermions $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus S \otimes R^*)$.
 \item a ghost field $c \in \Omega^0(\RR^3; \gg)[1]$.
\end{itemize}

@@

\vspace{-10pt}
\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\spin(3;\CC)$.  
The fields are:
\begin{itemize}
 \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
 \item matter bosons $\phi \otimes v \in \Omega^0(\RR^3; W \otimes U)$.
 \item gauge fermions $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes (W \oplus W) \otimes \gg)$.
 \item matter fermions $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
 \item a ghost field $c \in \Omega^0(\RR^3; \gg)[1]$.
\end{itemize}

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=8$ supersymmetric Yang--Mills theory by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\spin(3;\CC)$.  
The fields are:
\begin{itemize}
 \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and scalar fields $\phi_j \in \Omega^0(\RR^3; \gg)$, $j=1,\ldots, 7$.
 \item gauge fermions $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$, $i=1,\ldots, 8$.
 \item a ghost field $c \in \Omega^0(\RR^3;\gg)[1]$.
\end{itemize}

@@

\section{Dimension 2}
The odd part of the $2$-dimensional supersymmetry algebra is 
\[
\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_- .
\]
The complex semi-spin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality.

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(2;\CC)$.  
In any case, the fields we obtain are
\begin{itemize}
 \item gauge bosons $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(a, \Bar{a}) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
 \item matter bosons $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
 \item gauge fermions $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; (S_+ \otimes W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
 \item matter fermions $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus (S_+ \oplus S_-) \otimes R^*)$.
 \item a ghost field $c \in \Omega^0(\RR^2; \gg)[1]$.
\end{itemize}

@@

\begin{theorem} \label{2d_minimal_twist_thm}
The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with matter valued in a complex $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.  
Moreover, this equivalence is $\mr U(1)$-equivariant.
\end{theorem}

@@

\begin{itemize}
\item gauge bosons $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $a \in \Omega^0(\CC ; \fg)[2]$, $\Tilde{a} \in \Omega^0(\CC ; \fg)[2]$. 
\item gauge fermions $\lambda_0 \in \Omega^{0}(\CC ; \fg)[-1]$, $\chi_{0,1} \in \Omega^{0,1}(\CC ; \fg) [1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg)[1]$, $\Tilde{\lambda}_0 \in \Omega^0(\CC ; \fg) [3]$.
 %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
 \item matter bosons $\gamma_0 \in \Omega^0(\CC ; R)$, $\phi \in \Omega^0(\CC ; R^*)$;
 %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
 \item matter fermions $\gamma_{0,1} \in \Omega^{0,1}(\CC ; R)[-1]$, $\Tilde{\psi}_0 \in \Omega^0(\CC ; R)[1]$, $\beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)[-1]$, $\psi \in \Omega^0(\CC ; R^*)[1]$; 
 \item a ghost field $c \in \Omega^0(\RR^2; \fg)[1]$.
\end{itemize}
%We write the antifields similarly: the antifield of a field $x_n$ is written $x^*_{-n}$, with opposite $\mr U(1)$-weight.

@@

\begin{theorem} \label{2d_2_A_twist_thm}
The topological 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory with matter valued in a complex $\fg$-representation $R$ with respect to the family of square-zero supercharges $Q_t$ is perturbatively equivalent to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.  
This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\begin{theorem} \label{2d_2_B_twist_thm}
The topological B-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$.  This equivalence is $\mr U(1)$-invariant.
\end{theorem}

\begin{proof}
The theory is obtained as the dimensional reduction of the minimal twist of 3d $\mc N=2$ supersymmetric Yang--Mills theory in a non-invariant direction.  
Combining Theorem \ref{3d_minimal_twist_thm} and Proposition \ref{CS_diml_red_prop} we obtain the desired result.
\end{proof}

@@

The R-symmetry group is $G_R = \SU(2) \times \spin(4;\CC)$ whose action on $\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_-$ can be described as follows.
We can identify $W_\pm = S^4_\pm \otimes W_+^6$, where $W_+^6$ is the auxiliary space of 6d $\cN=(1,0)$ supersymmetry, and $S^4_\pm$ are the semi-spin representations of $\spin(4;\CC)$. 
The group $\spin(4;\CC)$ acts on $S^4_\pm$ in the natural way, and $\SU(2)$ acts on $W_+^6 \cong \CC^2$ as the fundamental representation.

@@

\begin{theorem}
The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic $BF$ theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$. 
This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\begin{theorem}
The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in symplectic $\fg$-representation $U$ admits a one-parameter deformation to the A-twist.  
This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.   This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\begin{theorem}
The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to topological $BF$ theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.  This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\begin{prop}
There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra, which we will refer to as the $A$- and $B$-supercharges.  The $B$-supercharge occurs as a degeneration of $A$-type supercharges.
\end{prop}

\begin{proof}
We classify $\spin(8;\CC)$-orbits in the space of pairs of non-zero null-vectors $w_+ \in W_+$ and $w_- \in W_-$.  Since $\spin(8;\CC)$ acts transitively on the possible choices of $w_+$, it remains for us to understand the action of the stabilizer $\stab(w_+) \sub \spin(8;\CC)$ on the space of null vectors $w_-$.  The element $w_+$ is equivalent to the data of a Lagrangian subspace $L \sub V_8$, along with a half-density.  As a representation of the subgroup $\mr{ML}(L)$ of $\stab(w_+)$, the two semispin representations decompose as
\begin{align*}
 W_+ &\iso (\CC \oplus \wedge^2 L \oplus \wedge^4 L) \otimes \det(L)^{-1/2} \\
 W_- &\iso (L \oplus \wedge^3 L) \otimes \det(L)^{-1/2},
\end{align*}
with $w_+ \in \wedge^4 L$.  With respect to this decomposition, say $w_- = (v_1,v_3)$.  If $v_1 \ne 0$, then we can act by $\wedge^2 L \sub \stab(w_+)$ to make $v_3 = 0$.  Under the action of $\SL(L)$ all such non-zero $v_1$ are in the same orbit.  Likewise if $v_1 = 0$ then $v_3 \ne 0$ and we can act by $\SL(L)$ to see that all such non-zero $v_3$ are in the same orbit.  There are, therefore, two orbits once again, with one degenerating to the other.
\end{proof}

Upon dimensional reduction from 3d $\mc N=8$, the $B$-supercharge reduces to the 2d $\mc N=(8,8)$ $B$-supercharge. 
Indeed, if we forget down to $\mc N=4$ supersymmetry, then the $B$-twist should correspond to the $B$-twist.  In both $\mc N=(4,4)$ and $\mc N=(8,8)$ the two orbits are distinguished, in that the orbit of $B$-twists lies in the closure of the orbit of $A$-twists.

@@

\begin{theorem}
The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills admits a one-parameter deformation to the $A$-twist.  This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.   This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

We turn to $\cN=(0,2)$ supersymmetric Yang-Mills theory.
Here, $W_+ = 0$ and $W_-$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
The supersymmetric matter consists of the $\cN = (0,2)$ chiral multiplet with values in a representation $R$. 
The $R$-symmetry group is $G_R = \spin(2;\CC)$ which acts on $W_-$ by the defining representation.

The untwisted fields are given by:
\begin{itemize}
\item a gauge boson $A \in \Omega^1(\RR^2;\fg)$.
\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
\item matter bosons $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
\item matter fermions $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R)$.
\item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
\end{itemize}
The field $\lambda$ transforms in the defining representation of $G_R = \spin(2; \CC)$.
The fields $\psi, \Bar{\psi}$ have weights $-1,+1$ respectively under $G_R \cong \CC^\times$.
